RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2014-01-04 papers/rjournal/eddelbuettel-francois-stokely.Rnw
Submit dirk's rewrite of acknowledgments section.  Add todo about OpenGPU or Poly at the bottom.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@699 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Table~\ref{tab:compression} shows the sizes of 50 sample R datasets as
returned by object.size() compared to the serialized sizes.
The summary compression sizes are listed below, and a full table for a
sample of 50 datasets is included on the next page.  Sizes are comparable
but protocol buffers provide simple getters and setters in multiple
languages instead of requiring other programs to parse the R
serialization format \citep{serialization}.  One takeaway from this
table is that RProtoBuf does not in general provide any significant
space-savings over R's normal serialization mechanism.  The benefit
from RProtoBuf comes from its interoperability with other
environments.

@@

@@

\CRANpkg{RProtoBuf} was originally written in 2009 by Romain
Fran\c{c}ois and Dirk Eddelbuettel.  The authors would particularly
like to thank Romain for his initial implementation and continued
design discussions. Several features of this package are based
on the design of the \CRANpkg{rJava} package by Simon Urbanek
(dispatch on new, S4 class structures using external pointers). We'd
like to thank Simon for his indirect involvment on
\CRANpkg{RProtoBuf}.  The user defined table mechanism, implemented by
Duncan Temple Lang for the purpose of the \pkg{RObjectTables}
package allowed the dynamic symbol lookup. Many thanks to Duncan for
this amazing feature.  Kenton Varda was generous with his time in
reviewing code and explaining obscure protocol buffer semantics.  Karl
Millar and Jeroen Ooms were helpful in reviewing code or offering
suggestions.  Saptarshi Guha's contemporaneous work on \pkg{RHIPE} was a
strong motivator.

>>>>

Table~\ref{tab:compression} shows the sizes of 50 sample R datasets as
returned by object.size() compared to the serialized sizes.
The summary compression sizes are listed below, and a full table for a
sample of 50 datasets is included on the next page.  Sizes are comparable
but protocol buffers provide simple getters and setters in multiple
languages instead of requiring other programs to parse the R
serialization format \citep{serialization}.  One takeaway from this
table is that RProtoBuf does not in general provide any significant
space-savings over R's normal serialization mechanism.  The benefit
from RProtoBuf comes from its interoperability with other
environments, safe versioning,

@@

TODO(mstokely): Talk about Jeroen Ooms OpenCPU, or talk about Andy
Chu's Poly.

@@

The first versions of \CRANpkg{RProtoBuf} were written during 2009-2010,
with very significant contributions, both in code and design, made by
Romain Fran\c{c}ois. His continued influence on design and code is
appreciated. Several features of the package are influenced
by on the design of the \CRANpkg{rJava} package by Simon Urbanek
The user-defined table mechanism, implemented by Duncan Temple Lang for the
purpose of the \pkg{RObjectTables} package allowed the dynamic symbol lookup.
Kenton Varda was generous with his time in reviewing code and explaining
obscure protocol buffer semantics.  Karl Millar and Jeroen Ooms were
helpful in reviewing code or offering suggestions.  The contemporaneous
work by Saptarshi Guha on \pkg{RHIPE} was a strong initial motivator.
